State of the Practice for Medical Imaging Software

### 2022-03-23 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Revisions to SOP for MI paper, mostly in Methodology section

\begin{enumerate}
\item Identify list of representative software packages
(Section~\ref{sec_software_selection});
\item Measure (or grade) the selected software (Section~\ref{sec_grading_software});
\item Interview developers (Section~\ref{sec_interview_methods}).
\item Answer the research questions (as given in Section~\ref{sec_motivation})
\end{enumerate}

@@

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process cannot put to much of a burden
on their time.  For the current assessment, our Domain Expert (and paper
co-author) is Dr.\ Michael Noseworthy, Professor of Electrical and Computer
Engineering at McMaster University, Co-Director of the McMaster School of
Biomedical Engineering, and Director of Medical Imaging Physics and Engineering
at St. Joseph's Healthcare, Hamilton, Ontario, Canada.

@@

We initially identified 48 MI candidate software projects from the literature
\citep{Bjorn2017, Bruhschwein2019, Haak2015}, online articles \citep{Emms2019,
Hasan2020, Mu2019}, and forum discussions \citep{Samala2014}.  The full list of
48 packages is available in \citet{Dong2021}.  To reduce the length of the list
to a manageable number (29 in this case), we filtered the original list as
follows:

@@

\item We removed \textit{Open Dicom Viewer}, since it has not received any
updates for a long time (since 2011).

@@

We grade the selected software using the measurement template summarized
in~\citet{SmithEtAl2021}.  The template summarizes measures of the qualities
listed in Section~\ref{sec_software_quality}, except for reproducibility, which
is assessed through the developer interviews
(Section~\ref{sec_interview_methods}). For each software package, we fill-in the
template questions. This process can take between 1 to 4 hours for each package.
Project developers can be contacted for help regarding installation, if
necessary, but a cap of about 2 hours is imposed on the
installation process, to keep the overall measurement time feasible. An excerpt
of the spreadsheet is shown in Figure~\ref{fg_grading_template_example}.
\wss{The Figure should be updated to be easier to read.}  A column is included
to for each measured software package.

\begin{figure}[!ht]
\includegraphics[scale=0.42]{figures/template.png}
\caption{Grading template example}
\label{fg_grading_template_example}
\end{figure}

>>>>

\begin{enumerate}
\item Identify list of representative software packages
(Section~\ref{sec_software_selection});
\item Measure (or grade) the selected software
(Section~\ref{sec_grading_software});
\item Interview developers (Section~\ref{sec_interview_methods});
\item Answer the research questions (as given in Section~\ref{sec_motivation}).
\end{enumerate}

@@

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process cannot put to much of a burden
on their time.  For the current assessment, our Domain Expert (and paper
co-author) is Dr.\ Michael Noseworthy, Professor of Electrical and Computer
Engineering at McMaster University, Co-Director of the McMaster School of
Biomedical Engineering, and Director of Medical Imaging Physics and Engineering
at St.\ Joseph's Healthcare, Hamilton, Ontario, Canada.

@@

We initially identified 48 MI candidate software projects from the literature
\citep{Bjorn2017, Bruhschwein2019, Haak2015}, online articles \citep{Emms2019,
Hasan2020, Mu2019}, and forum discussions \citep{Samala2014}.  The full list of
48 packages is available in \citet{Dong2021}.  To reduce the length of the list
to a manageable number (29 in this case, as given in Section~\ref{ch_results}),
we filtered the original list as follows:

@@

\item We removed \textit{Open Dicom Viewer}, since it has not received any
updates in a long time (since 2011).

@@

We grade the selected software using the measurement template summarized
in~\citet{SmithEtAl2021}.  The template provides measures of the qualities
listed in Section~\ref{sec_software_quality}, except for reproducibility, which
is assessed through the developer interviews
(Section~\ref{sec_interview_methods}). For each software package, we fill-in the
template questions. This process can take between 1 to 4 hours for each package.
Project developers can be contacted for help regarding installation, if
necessary, but a cap of about 2 hours is imposed on the installation process, to
keep the overall measurement time feasible. An excerpt of the spreadsheet is
shown in Figure~\ref{fg_grading_template_example}.  A column is included for
each measured software package.

\begin{figure}[!ht]
\includegraphics[scale=0.67]{figures/template.pdf}
\caption{Grading template example}
\label{fg_grading_template_example}
\end{figure}
